Merging in R

### 2022-10-25 text/05/MergingInR.Rmd
Removed backslashes
Added "Being updated" tags to 2005 files

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- R software
output: html_document
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here\'s a simple example of how this would work.

>>>>

---
title: Merging in R
author: Steve Simon
date: 2005-07-26
categories:
- Blog post
tags:
- Being updated
- R software
output: html_document
---
Merging is tricky in any program, and you have to be sure that you know
what you are doing. I have found that keeping an index variable will
allow me to backtrack and find information in the original files if
needed. Here's a simple example of how this would work.
